Quality Assesment of OpenStreetMap Footpath Data for 3D City Modelling

### 2020-05-10 report/report.tex
Fix reference to Trafikverket

The default minimum widths were obtained from (Lantmäteriet, 20). The standard recommended minimum width for a two-lane road in Sweden is 6.5 meters.
Subsequent visual measurements of a few key locations in the Stockholm area revealed the following minimum way widths:
Table \ref{table:road-widths} shows the minimum and maximum road widths that were found during these measurements, and that will be used in the collision study.

@@

\bibitem{trafikverket-20}
https://trafikverket.ineko.se/Files/sv-SE/71830/Ineko.Product.RelatedFiles/2020\_029\_vagar\_och\_gators\_utformning\_krav.pdf \\

>>>>

The default minimum widths were obtained from (Trafikverket, 20). The standard recommended minimum width for a two-lane road in Sweden is 6.5 meters.
Subsequent visual measurements of a few key locations in the Stockholm area revealed the following minimum way widths:
Table \ref{table:road-widths} shows the minimum and maximum road widths that were found during these measurements, and that will be used in the collision study.

@@

\bibitem{trafikverket-20}
Trafikverket. (2020). Vägars och gators utformning. Publikation 2020:029. \\
https://trafikverket.ineko.se/Files/sv-SE/71830/ \\
Ineko.Product.RelatedFiles/2020\_029\_vagar\_och\_gators\_utformning\_krav.pdf
